---
title: "analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette demonstrates how to analyze your financial transactions using the `transactions` dataset. 
We will generate useful insights such as net worth over time, cash flow analysis, and income and expenses trends.

# Prerequisites

Load the required packages:

```{r setup}
library(tidyverse)
library(plotly)
# library(cashier)
devtools::load_all()
```

# Loading the Transactions Data

First, let's load the `transactions` dataset:

```{r load data}
data("sample_transactions")
head(transactions)
```

# Net Worth

Now for a start, we will calculate the net worth over time, i.e. the cumulative 
sum of the total transaction amounts:

```{r example}
net_worth <- transactions |> calculate_net_worth()
net_worth |> filter(account_name == "Net Worth") |> plot_net_worth()
net_worth |> plot_net_worth()
```

Now we plot the cash flow:

```{r}
plot_cash_flow(transactions)
```
