---
title: "import"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{import}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette provides an overview of the `process_csv` function, which 
is designed to import and preprocess financial transaction data from a CSV file. 
This function handles tasks such as reading data, cleaning, and renaming columns, 
making it easier for you to analyze your financial data.

# Prerequisites

Load the required packages:

```{r setup}
library(tidyverse)
# library(cashier)
devtools::load_all()
```

# Function Overview

The `process_csv` function performs the following tasks:

1. Imports Data: Reads financial transactions from a CSV file.
2. Handles Locale Settings: Converts date formats, decimal separators, and column types based on locale.
3. Renames Columns: Renames columns to shorter, more intuitive names.
4. Prepares Data: Ensures the data is ready for further analysis.

# Arguments

- `file_path`: The file path to the CSV file containing your transaction data. 
This file should be formatted with `;` as a separator, `,` as a decimal mark, 
and dates in `dd.mm.yyyy` format.

# Details

The `process_transactions` function reads a CSV file containing financial transactions and performs several key operations to ensure the data is in a usable format. Specifically:

- Locale Handling: Since the CSV uses a comma as a decimal mark and a period as a grouping mark, the locale() function is used to correctly interpret these values during import.
- Column Renaming: After loading the data, the columns are renamed to shorter, more descriptive names to make further analysis easier.
- Date Parsing: Dates are automatically parsed into Date objects.

# Example Usage

Suppose you have a CSV file named `transactions.csv`. You can process this file as follows:

```{r example usage}
# Path to your CSV file
file_path <- "../inst/extdata/sample_transactions.csv"

# Process the transactions
transactions <- process_csv(file_path)

# View the first few rows of the processed data
head(transactions)
```
